Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-08 doc/paper.tex
tables prepared

	In order to enable fast calculation of greedy functions described in previous subsections, we introduce several useful structures and auxiliary functions:
	\begin{itemize}
		\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point;
		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of Guards in solution which are visible from that point;
		\item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution;
		\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from partial solution.
	\end{itemize}
	\begin{algorithm}[!t]
          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsAdd}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} vertex $v$
          		\State \textbf{Output:} updated structures: coveredPoints and numberOfGuards
          		\For{$p$ in $S[v]$}
          		\State coveredPoints.insert($p$)
          		\State numberOfGuards.find($p$).second++
          		\EndFor
          	\end{algorithmic}
          \end{algorithm}
                    \begin{algorithm}[!t]
          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsRemove}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} vertex $v$
          		\State \textbf{Output:} updated structures coveredPoints and numberOfGuards
          		\For{$p \in S[v]$}
          		\State numberOfGuards.find($p$).second-- --
                \If {numberOfGuards.find($p$).second$=0$}
                    \State coveredPoints.remove($p$)
                    \EndIf
          		\EndFor
          	\end{algorithmic}
          \end{algorithm}

\subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}  
	The performance of \textrm{Cplex}  soon or later degrades w.r.t. instance size since the prolem is NP--hard. On the other hand, in the later stage, there is an increased chance for Greedy to worsen the final greedy solution due to a high number of components which are similar to be chosen for extension. So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few interactions  and only then to use CPLEX to do the completion of the partial solution. In details, our approach consists of the following steps:
	\begin{enumerate}
		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $s^{ps}$ (therefore, $|s^{ps}| = K$);
		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via CPLEX:
		\begin{itemize}
			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model;
			\item a complete solution $\bar {s^p}$ is obtained;
		\end{itemize}
		\item Return $f(\bar {s^p})$.
	\end{enumerate}

@@

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
        \end{itemize}  and 6 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}

>>>>

	In order to enable fast calculation of greedy functions described in previous subsections, we introduce several useful structures and auxiliary functions:
	\begin{itemize}
		\item structure \texttt{map<Point,list<Point>> Visibility} -- for each point of $D(P)$, we provide the list of guards which are visible from that point;
		\item structure \texttt{map<Point,int> numberOfGuards} -- for each point from $D(P)$,  we keep the number of Guards in solution which are visible from that point;
		\item structure \texttt{set<Point> CoveredPoints} -- set of points covered by the partial solution;
		\item function \texttt{updateCoveredPointsAdd (vertex v)} -- does the update of  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by considering all new points which are covered by vertex \texttt{v}, when \texttt{v} is added to solution; pseudocode of the procedure is shown in Algorithm \ref{alg:updateCoveredPointsAdd}. Its time complexity is $O(n)$.  
		%\item function \texttt{updateCoveredPointsRemove(vertex v)} -- updates  structures \texttt{CoveredPoints} and \texttt{numberOfGuards} by removing all points which are covered by \texttt{v}, when \texttt{v} is removed from partial solution.
	\end{itemize}

	\begin{algorithm}[!t]
          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsAdd}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} vertex $v$
          		\State \textbf{Output:} updated structures: coveredPoints and numberOfGuards
          		\For{$p$ in $S[v]$}
          		\State coveredPoints.insert($p$)
          		\State numberOfGuards.find($p$).second++
          		\EndFor
          	\end{algorithmic}
          \end{algorithm}

            \begin{algorithm}[!t]
          	\caption{Function updateCoveredPointsAdd}\label{alg:updateCoveredPointsRemove}
          	\begin{algorithmic}[1]
          		\State \textbf{Input:} vertex $v$
          		\State \textbf{Output:} updated structures coveredPoints and numberOfGuards
          		\For{$p \in S[v]$}
          		\State numberOfGuards.find($p$).second-- --
                \If {numberOfGuards.find($p$).second$=0$}
                    \State coveredPoints.remove($p$)
                    \EndIf
          		\EndFor
          	\end{algorithmic}
          \end{algorithm}
	  \end{comment} 
\subsubsection{A Hybrid of the \textsc{Greedy + Cplex}}  
	The performance of \textrm{Cplex}  soon or later degrades w.r.t. instance size since the prolem is NP--hard. On the other hand, in the later stage, there is an increased chance for Greedy to worsen the final greedy solution due to a high number of components which are similar to be chosen for extension. So, it makes sense to combine  partial solutions generated with a Greedy procedure over a few interactions  and only then to use CPLEX to do the completion of the partial solution. In details, our approach consists of the following steps:
	\begin{enumerate}
		\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $s^{ps}$ (therefore, $|s^{ps}| = K$);
		\item Take solution $s^{ps}$ and make it complete by solving a corresponding submodel via CPLEX:
		\begin{itemize}
			\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{i} = 1$, for all $v_i \in s^{ps}$ into the existing WOAGP model;
			\item a complete solution $\bar {s^p}$ is obtained;
		\end{itemize}
		\item Return $f(\bar {s^p})$.
	\end{enumerate}

@@

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
        \end{itemize}  and 6 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}
         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.

         \begin{table}
         \centering
         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
         	\hline
         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
         	\hline
            \multicolumn{1}{|c|}{}&
            \multicolumn{2}{|c|}{$Small$}&
            \multicolumn{2}{|c|}{$Large$} \\
            \hline	
         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
            \textsc{Cplex} & & & & \\ \hline
            \textsc{Cp} & & & & \\ \hline
         	\textsc{Greeedy-1} & & & & \\ \hline
         	\textsc{Greeedy-2} & & & & \\ \hline
         	\textsc{Greeedy-3} & & & & \\ \hline
         	\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
         	\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
         	\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
         	\hline
         \end{tabular}
         \caption{Different combinations of the algorithms.}
        \end{table}

       \begin{table}
    	\centering
    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
    		\hline
    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
    		\hline
    		\multicolumn{1}{|c|}{}&
    		\multicolumn{2}{|c|}{$Small$}&
    		\multicolumn{2}{|c|}{$Large$} \\
    		\hline	
    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
    		\textsc{Cplex} & & & & \\ \hline
    		\textsc{Cp} & & & & \\ \hline
    		\textsc{Greeedy-1} & & & & \\ \hline
    		\textsc{Greeedy-2} & & & & \\ \hline
    		\textsc{Greeedy-3} & & & & \\ \hline
    		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
    		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline
    		\textsc{Greeedy-3 + Cplex} & & & & \\ \hline
    		\hline
    	\end{tabular}
    	\caption{Different combinations of the algorithms.}
    \end{table}
